\documentclass[a4paper,10pt]{article}

% ================= PACKAGES =================
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[left=0.4in,right=0.4in,top=0.4in,bottom=0.4in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{linkblue}{HTML}{0645AD}
\hypersetup{
    colorlinks=true,
    urlcolor=linkblue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{2pt}
\setlist[itemize]{noitemsep,topsep=1pt,leftmargin=0.2in}

\begin{document}

% ================= HEADER =================
\begin{center}
{\Large \textbf{Md Sahebuddin Ansari}}\\
\vspace{2pt}
{\large \textbf{Full-Stack Software Engineer}} \\
\vspace{2pt}
+91-9113111384 \quad|\quad
\href{mailto:sahebcoder@gmail.com}{sahebcoder@gmail.com} \quad|\quad
Kolkata, India \\
\vspace{2pt}
\href{https://linkedin.com/in/saheb142003}{linkedin.com/in/saheb142003} \quad|\quad
\href{https://github.com/Saheb142003}{github.com/Saheb142003} \quad|\quad
\href{https://saheb142003.netlify.app}{saheb142003.netlify.app}
\end{center}

% ================= SUMMARY =================
\vspace{-5pt}
\section*{Summary}
Results-driven Full-Stack Software Engineer specializing in scalable backend infrastructure, REST APIs, and AI-powered web applications. Proven expertise in architecting production-grade MERN stack platforms with optimized database schemas, secure authentication, and real-time capabilities. Dedicated to software efficiency, modular design, and delivering high-quality user experiences.

% ================= SKILLS =================
\section*{Skills}
\textbf{Programming Languages:} JavaScript (ES6+), Python, C, C++ \\
\textbf{Frontend:} HTML5, CSS3, React.js, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, RESTful APIs, WebSockets, JWT, OAuth \\
\textbf{Databases:} MongoDB, MySQL, Redis \\
\textbf{Tools \& Platforms:} Git, GitHub, Docker, CI/CD \\
\textbf{Core Competencies:} Data Structures \& Algorithms, System Design, API Development, Authentication, Database Design, Performance Optimization, Agile Collaboration

% ================= EXPERIENCE & PROJECTS =================
\section*{Experience \& Projects}

\textbf{\href{https://learnstream.netlify.app/}{AI-Driven Learning Management System}} \hfill \href{https://github.com/Saheb142003/LearnStream}{GitHub}
\begin{itemize}
\item \textbf{Engineered} a full-stack learning platform to transform YouTube transcripts into interactive quizzes and structured educational modules.
\item \textbf{Designed} and deployed 30+ RESTful APIs for identity verification, dynamic content generation, analytics, and user progress tracking.
\item \textbf{Architected} optimized MongoDB schemas, maximizing query throughput and data retrieval efficiency.
\end{itemize}

\textbf{\href{https://book-reselling-app.vercel.app/explore}{Book Reselling App}} \hfill \href{https://github.com/Saheb142003/Book-Reselling-App}{GitHub}
\begin{itemize}
\item \textbf{Built} a full-stack book reselling platform with authentication, role-based logins, and admin-controlled workflows.
\item \textbf{Implemented} secure buyer-seller interactions with automated order handling and platform-managed access control.
\item \textbf{Developed} a scalable marketplace flow for listing, exploration, and transaction management with a clean user experience.
\end{itemize}

\textbf{\href{https://cravespace.netlify.app}{Scalable Multi-Vendor Food Marketplace}} \hfill \href{https://github.com/Saheb142003/Restaurant-Management-System}{GitHub}
\begin{itemize}
\item \textbf{Developed} a high-performance marketplace connecting consumers with local restaurants, featuring dynamic listings and intuitive discovery tools.
\item \textbf{Built} 20+ modular APIs to handle advanced search algorithms, rating mechanisms, and robust content management systems.
\item \textbf{Implemented} efficient database indexing strategies and relational logic, reducing execution times and ensuring platform scalability.
\end{itemize}

% ================= OPEN SOURCE CONTRIBUTIONS =================
\section*{Open Source Contributions}
\begin{itemize}
\item \textbf{Shipped} multiple full-stack applications with integrated JWT security, analytics tracking, and responsive UI designs.
\item \textbf{Constructed} resilient backend services with streamlined API layers to ensure high availability and fault tolerance.
\item \textbf{Maintained} 20+ active repositories on \href{https://github.com/Saheb142003}{GitHub}, demonstrating strong version control proficiency and consistent collaborative development.
\end{itemize}

% ================= ACHIEVEMENTS =================
\section*{Achievements}
\begin{itemize}
\item \textbf{Solved} 450+ data structure and algorithm problems on \href{https://leetcode.com/u/saheb142003/}{LeetCode} with a 1500+ contest rating, showcasing strong analytical capabilities.
\item \textbf{Applied} core system design principles focusing on load optimization, code reusability, and long-term maintainability across independent projects.
\end{itemize}

% ================= EDUCATION =================
\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill 2022 -- 2026 \\
\href{https://jisuniversity.ac.in}{JIS University, Kolkata} \hfill 8.56 CGPA \vspace{3pt}

\textbf{Higher Secondary} \hfill 2020 -- 2022 \\
\href{https://drive.google.com/file/d/1NXPlnSnuPSRjS4P6Tt3J7UAzP7Mf2cbm/view?usp=sharing}{R.S. More College, Dhanbad} \hfill 86.60\% \vspace{3pt}

\textbf{Secondary} \hfill 2019 -- 2020 \\
\href{https://drive.google.com/file/d/16TLYYONeyLaemFxQTAiFGJXFBConsh8e/view?usp=sharing}{Roy Academy, Dhanbad} \hfill 85.20\%

% ================= INTERESTS =================
\section*{Interests}
Chess \& Strategic Games \quad|\quad Coding \& System Design \quad|\quad Scalable System Architectures

% ================= CERTIFICATIONS =================
\section*{Certifications}
\begin{itemize}
\item \href{https://udemy-certificate.s3.amazonaws.com/pdf/UC-53a9e3f1-cb41-4419-9419-d5271a67b741.pdf}{Udemy: Full Stack Web Development \quad |\quad} \href{https://learn.saylor.org/pluginfile.php/1/tool_certificate/issues/1763391491/0368517683MA.pdf}{Saylor: Building with AI \quad |\quad} \href{https://drive.google.com/file/d/1QZ_C8XfGIxVyAqLyvEtRDfPKWdStqbn-/view?usp=sharing}{IIT Kharagpur: Programming in Java}
\end{itemize}

\end{document}